---
title: "Assignment 1: R Markdown practice"
author: "Ahmed Dirar"
date: "`r Sys.Date()`"
documentclass: article
geometry: margin=1in
fontsize: 11pt
output:
  pdf_document:
    toc: false
    df_print: kable
    fig_caption: false
    number_sections: true
    dev: pdf
    highlight: tango
  html_document:
    theme: paper
    self_contained: true
    toc: false
    df_print: kable
    fig_caption: false
    number_sections: true
    smart: true
    dev: svg
urlcolor: blue
---

```{r setup, include=FALSE}
# Get GitHub username
if (.Platform$OS.type == "unix") {
  git_remote <- system('git config --get remote.origin.url', intern = TRUE)
  git_user <- (strsplit(git_remote, "assignment-1-") |> unlist())[2]
} else {
  git_remote <- shell('git config --get remote.origin.url', intern = TRUE)
  git_user <- (strsplit(git_remote, "assignment-1-") |> unlist())[2]
}
```

---
subtitle: "GitHub username: `r git_user`"
---
<!-- Write your Markdown below this line -->

<!-- # Hello World! -->

<!-- Try replacing # with ## in the RMarkdown file - what happens? -->

<!-- ## Hellow World v2! -->
<!-- It makes it got from 1 to 1.1 -->

# How the Course Works
it's great and all just got a lot to learn.

# Course Goals

By the end of the course, I should be able to:

* use [GitHub](https://github.com/M3do-1) for creating a reproducible research documnet.

  - My GitHub username is: [_M3do-1._](https://github.com/M3do-1)

* Obtain, clean, transform, and visualize a dataset using R Programming language.
* Interpret and predict dataset trends using statistical inference and models.
* Critically examin and interpret statistical claims reported in mass media.

# Including Code

## Running R code in a code chunk

```{r}
x <- 2 + 4
x + 9
```

The output of first line of code is not printed out because it is assigned to variable instead.
The second line of output is printed out instead, but this means that the calculated value has not been saved for future use.

## Displaying Graphs
```{r}
plot(x = iris$Sepal.Length, y = iris$Sepal.Width)
```
